% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments


In the first place I wish to thank my supervisors,
Robert Wilson and John Bray. I am grateful to Rob for the 
wisdom he shared with me, for his ability to shape ideas,
and for warm and enlightening discussions. I likewise thank
John for his patience, excellent guidance, extensive
knowledge, and most importantly, for being a friend. I am also thankful to Leonard Soicher
for his kindness, willingness to help, 
and for providing an alternative perspective
on this thesis.

No less I wish to thank my sister Anna, her husband Edward, and my nephews Sofie and Darren, without whom 
this thesis would not have existed, and without whom I would
have not been myself. To my mother Galina I am thankful for her love,
support, and faith in me throughout my whole life. 

I wish to thank Alex Fink, Katie Hale, Gabriella Caminotto, and my friends 
Dominic Carter, Alexander Luzgarev, and many others for their unconditional kindness 
and for being there for me. 

Finally, I am grateful to my colleagues
at the School of Mathematical Sciences for their friendliness
and good sense of humour which made my time as a PhD student
a most enjoyable one. 


\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
